Robust Agglomeration of Labeled Neurons using 3D Skeletonization

### 2017-11-01 papers/cvpr2018/1_related_work.tex
papers: updated related work

These above neural networks generate probabilities that neighboring voxels belong to the same neuron.
Many algorithms work at a level above these networks and train random-forest classifiers to produce segmentations of the EM images where every unique neuron in the volume has a unique label~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image} (CITE NEUROPROOF).

Despite the successes of these algorithms they often make early local mistakes leading to errors in the segmentation. Proofreading methods create a "human-in-the-loop" framework that allows users to find errors and correct them \cite{haehn2017scalable,haehn2017guided,haehn2014design}. Flood-filling networks merge these two steps by training an end-to-end network that takes as input raw image data and produces a segmentation \cite{januszewski2016flood}. Although these networks have produced impressed segmentation accuracies, they are currently too slow for large scale connectomics reconstructions.

ADD SECTION ON CORRECTING SPLIT ERRORS

The fields of computer graphics, mathematics, and biomedical visualization have produced extensive research into the skeletonization of 3D binary volumes. A large amount of research has explored topologically consistent thinning algorithms and potential medical applications of these methods \cite{palagyi20003d,palagyi2001sequential}. In computer graphics, fast medial axis algorithms allow animators to quickly move characters through successive frames \cite{baran2007automatic,bharaj2012automatically}. The Tree-structure Extraction Algorithm for Accurate and Robust Skeletons (TEASER) has been used by connectomics researchers to parameterize 3-D shapes \cite{sato2000teasar,zhao2014automatic}.

ADD SECTION ON LEARNED SHAPE FEATURES

ADD SECTION ON GRAPH PARTITIONING

>>>>

These above neural networks generate probabilities that neighboring voxels belong to the same neuron.
Many algorithms work at a level above these networks and train random-forest classifiers to produce segmentations of the EM images where every unique neuron in the volume has a unique label~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image} (CITE NEUROPROOF). 
Despite the success of these classifiers, they often make mistakes based on the local information leading to errors in the segmentation. 
Proofreading methods create a ``human-in-the-loop" framework that allows users to find errors and correct them \cite{haehn2017scalable,haehn2017guided,haehn2014design,DBLP:journals/corr/abs-1708-02599}. 
More recently, flood-filling networks merge the process of generating voxel affinities and then producing segmentations by training an end-to-end neural network that outputs segmentations~\cite{januszewski2016flood}. 
Although these networks produce impressive segmentation accuracies, they are currently too slow for large scale connectomics reconstructions.

Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally}. 
The multicut graph partitioning algorithm extracts segments the graph and remove edges such that there are no cycles. 
This closely resembles the biological constraint that neurons have a topological genus of zero. 
There are several useful multicut heuristics which provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis,kernighan1970efficient,keuper2015efficient}

A sizable amount of computer vision research analyzes various hand-designed shape features for determining similarity between objects~\cite{osada2002shape} and for segmentation\cite{conners1984segmentation}. 
Currently, the random-forest classifiers used in connectomics rely on hand-designed features to make merge decisions.
Some of these features encode the distribution of probabilities that voxels along a segment boundary belong to the same neuron as their neighbors~\cite{nunez2014graph,ren2003learning}.
However, there is evidence that machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.

The fields of computer graphics, mathematics, and biomedical visualization produce extensive research into the skeletonization of 3D binary volumes. 
Some of the research explores topologically consistent thinning algorithms and potential medical applications of these methods~\cite{palagyi20003d,palagyi2001sequential}. 
In computer graphics, fast medial axis algorithms allow animators to quickly move characters through successive frames~\cite{baran2007automatic,bharaj2012automatically}. 
In these works, the skeleton acts as the simplest representation of a 3-D volume. 
The Tree-structure Extraction Algorithm for Accurate and Robust Skeletons (TEASER) has been used by connectomics researchers to parameterize 3-D shapes~\cite{sato2000teasar,zhao2014automatic}.
